---
title: "Task 5 analysis"
author: "Harry Williams"
date: "11/11/2020"
output: html_document
---
## Packages
```{r}
library(tidyverse)
library(here)
```

## data 
```{r}
rwa_responses <- read_csv("clean_data/rwa_responses_clean")
```


# Q1 What’s the average RWA score for each gender?
```{r}
rwa_responses %>% 
  group_by(gender) %>% 
  summarise(avg_score = mean(score))
```

# Q2 What’s the average RWA score for left handed people vs. right handed people.
```{r}
rwa_responses %>% 
  group_by(hand) %>% 
  summarise(avg_score = mean(score))
```

# Q3 What’s the average family size for each type of childhood?
```{r}
rwa_responses %>% 
  group_by(urban) %>% 
  summarise(avg_score = mean(score))
```

# Q4 What’s the average time to take the test for each education level?
```{r}
education_time <- rwa_responses %>% 
  group_by(education) %>% 
  summarise(avg_score = mean(total_time_taken))

education_time
```

# Q5 Create a plot of results of question 4.
```{r}
education_time %>% 
  ggplot(aes(  education, avg_score)) + geom_bar(stat="identity")
```

rwa_responses %>% 
  group_by(education) %>% 
  summarise(avg_score = mean(total_time_taken))
What’s the average RWA score for people aged
Under 18
18 to 25
26 to 40
41 to 60
Over 60
```{r}
```{r}
```{r}
```


```{r}
```

```

```


