---
title: "Task 1 Analysis"
author: "Harry Williams"
date: "09/11/2020"
output: html_document
---
## Packages
```{r}
library(tidyverse)
library(here)
```

## Data
```{r}
decathlon_results <- read_csv(here("clean_data/clean_decathlon_results.csv"))
```

## Q1. Who had the longest long jump seen in the data?

```{r}
decathlon_results %>% 
  select(athlete, long_jump) %>% 
  slice_max(long_jump, n = 1)
```


## What was the average 100m time in each competition?
```{r}
decathlon_results %>% 
  group_by(competition) %>% 
  summarise(avg_100m_time = mean(x100m))
```

## Who had the highest total points across both competitions?
```{r}
decathlon_results %>% 
  group_by(athlete) %>% 
  summarise(total_points = sum(points)) %>% 
  slice_max(total_points, n = 1)
```

## What was the shot-put scores for the top three competitors in each competition?
### Decastar
```{r}
decathlon_results %>% 
  filter(competition == "decastar") %>% 
  select(athlete, shot_put) %>% 
  slice_max(shot_put, n = 3)
    
```
### Olympic Games
```{r}
decathlon_results %>% 
  filter(competition == "olympic_games") %>% 
  select(athlete, shot_put) %>% 
  slice_max(shot_put, n = 3)
    
```
## What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?
```{r}
decathlon_results %>% 
  mutate(x400m_time = ifelse(x400m < 50, "400m under 50 seconds", "400m over 50 seconds")) %>% 
  group_by(x400m_time) %>% 
  summarise(avg_points = mean(points))


```
