---
title: "Task 2 Analysis"
author: "Harry Williams"
date: "10/11/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages 
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
```

# Data
```{r, message=FALSE}
cake_ingredients <- read_csv(here("clean_data/cake_ingredients.CSV"))
```

The data comes from Table 12.8 in Chapter 12 of Hartigan (1975) on page 229. It gives a list of cakes and their ingredients. It also gives the quantities of each ingredient.

## Cleaning the data

The dataset was made long for better analysis. All the ingredients were listed as abbreviations so a second data set with the abbreviations were added. the Sour Cream measurement was changed to cup and eggs were changed to whole.

# Analysis

## Q1 - Which cake has the most cocoa in it?

```{r}
cake_ingredients %>%
  filter(ingredient == "cocoa") %>%
  slice_max(quantity)
```
One bowl chocolate cake had the most cocoa with 10 table spoons 

## Q2 - For sponge cake, how many cups of ingredients are used in total?

```{r, message=FALSE}
cake_ingredients %>%
  filter(cake == "sponge", measure == "cup") %>%
  group_by(cake) %>%
  summarise(total_cups = sum(quantity))
```

In sponge cake there were 3.5 cups worth of ingredients (not including teaspoon measurements).

## Q3 - How many ingredients are measured in teaspoons?

```{r}
cake_ingredients %>%
  filter(measure == "teaspoon") %>%
  distinct(ingredient) %>%
  summarise(number_of_ingredients_using_teaspoons = n())
```

In total 8 ingredient were measured in teaspoons.

## Q4 - Which cake has the most unique ingredients? 
This question was a bit ambiguous so two answers were given.

```{r, message=FALSE}
cake_ingredients %>%
  group_by(ingredient) %>%
  mutate(count = n()) %>% # find how many times each ingredient is used
  ungroup() %>%
  filter(count == 1) %>%
  group_by(cake) %>%
  summarise(number_of_unique_ingredients = n())
```
In total angel cake has the most number of unique ingredients.



```{r, message=FALSE}
cake_ingredients %>%
  group_by(cake) %>%
  summarise(number_of_ingredients = n()) %>%
  slice_max(number_of_ingredients)
```

Alternatively if the question is asking how many ingredients then babas au rhum and one bowl chocolate cake both contain the most number of ingredients 

## Q5 - Which ingredients are used only once?
```{r , message=FALSE}
cake_ingredients %>%
  group_by(ingredient) %>%
  summarise(number_of_times_used = n()) %>%
  filter(number_of_times_used == 1)
```

There are 8 ingredients which are only used once. 