---
title: "Task 1 Analysis"
author: "Harry Williams"
date: "09/11/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---

# Packages
```{r, message=FALSE}
library(tidyverse)
library(here)
```

# Data
```{r, message=FALSE}
decathlon_results <- read_csv(here("clean_data/clean_decathlon_results.csv"))
```

The data comes from 2 Decathlon competitions, Decastar and the Olympic Games. 

## Cleaning the data

The athletes names which were row titles were moved into their own column. The olympicg column became olympic_games for clarity.

# Analysis

## Q1. Who had the longest long jump seen in the data?

```{r}
decathlon_results %>%
  select(athlete, event, result) %>%
  filter(event == "long_jump") %>%
  slice_max(result, n = 1)
```

The athlete Clay had the longest jump of 7.96m.

## Q2. What was the average 100m time in each competition?

```{r, message = FALSE}
decathlon_results %>%
  filter(event == "x100m") %>%
  group_by(competition) %>%
  summarise(avg_100m_time = mean(result))
```

The Olympic Games had the fastest average 100m time. This is not surprising as the Olympics are the most important event for a decathlete.


## Q3. Who had the highest total points across both competitions?

```{r, message=FALSE}
decathlon_results %>%
  distinct(athlete, competition, points) %>% 
  group_by(athlete) %>%
  summarise(total_points = sum(points)) %>%
  slice_max(total_points, n = 1)
```
The athlete Sebrle has the highest number of points across both competitions. With over 17110 points.


## Q4. What was the shot-put scores for the top three competitors in each competition?
### Decastar

```{r, message=FALSE}
decathlon_results %>%
  filter(competition == "decastar" & event == "shot_put") %>%
  select(athlete, event, result) %>%
  slice_max(result, n = 3)
```

### Olympic Games

```{r,message=FALSE}
decathlon_results %>%
  filter(competition == "olympic_games" & event == "shot_put") %>%
  select(athlete, event, result) %>%
  slice_max(result, n = 3)
```


Sebrle and Karpov both appear in the top 2 across both competitions. With Sebrle being the better competitor across both.

## Q5. What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r, message=FALSE}
decathlon_results %>%
  filter(event == "x400m") %>%
  mutate(x400m_time = ifelse(result < 50, "400m under 50 seconds", "400m over 50 seconds")) %>%
  group_by(x400m_time) %>%
  summarise(avg_points = mean(points))
```
Those running the 400m in under 50 seconds scored more points than those who ran a total time of over 50 seconds.
